---
title: "Estatistica descritiva"
author: "Francisco Foz""
date: "Fevereiro, 2023"
output: html_document
---

# Estatística descritiva - Spaceship Titanic

## Importando bibliotecas

```{r}
library(dplyr)

```

## Importando dados

```{r}
df_train <- read.csv("https://raw.githubusercontent.com/FranciscoFoz/math-stats-training/main/spaceship-titanic/train.csv")
df_train
```

## Visualizando dados tabulares

### Head

```{r}

head(df_train,10)
```

### Select

```{r}
select(df_train,HomePlanet)
```

### Unique

```{r}
unique(select(df_train,HomePlanet))
```

### Arrange

```{r}
arrange(unique(select(df_train,Age)))
```

```{r}
arrange(df_train,Age)

```

### C

```{r}

c(unique(select(df_train,HomePlanet)))
```

```{r}
c(1,2,3,4,5,6,7,8,9)
```

```{r}
c(unique(select(df_train,Age)))
```

### Sprintf

```{r}
sprintf('O valor gasto em serviços de quarto é de %s até %s (valor da moeda corrente)',
        min(df_train$RoomService),max(df_train$RoomService))
```

*Mesma coisa só que com Glue:*

![]()

```{r}
library(glue)

glue('O valor gasto em serviços de quarto é de {min(df_train$RoomService)} até {max(df_train$RoomService)} (valor da moeda corrente)')
```

## Distribuição de Frequências

```{r}
table(df_train$HomePlanet)

```

```{r}
prop.table(table(df_train$HomePlanet)) * 100
```

```{r}

freq_homeplanet <- cbind(freq = table(df_train$HomePlanet), 
                  percent = prop.table(table(df_train$HomePlanet)) * 100)
freq_homeplanet
```

```{r}

colnames(freq_homeplanet) <- c('Frequência', 'Porcentagem (%)')
freq_homeplanet
```

```{r}
rownames(freq_homeplanet) <- c('Não identificado','Terra', 'Europa','Marte')
freq_homeplanet
```

```{r}

frequencia <- table(df_train$Transported,df_train$HomePlanet)
frequencia
```

```{r}
percentual <- prop.table(frequencia) *100
percentual
```

```{r}
tapply(df_train$Age,
       list(df_train$HomePlanet,df_train$Transported),mean)
```

```{r}

```

\

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
